HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
minor changes, mostly to figure1

{\small
\begin{tabular}{|l|l|l|l|}
\hline
L & Linker &  A & Participant \\
H & Scene & R & Relator \\
P & Process & C & Centre \\
\hline
\end{tabular}
}
    \end{center}
\caption{\label{fig:ucca_example_v2}
  Sample UCCA annotation where leaves correspond to words and nodes to units.
  Edge labels mark UCCA categories, listed  in the table.}
%which are largely ignored in this work
\end{figure}

@@

In Figure~\ref{fig:hume_tree_v2} we can see an example of a possible HUME
annotation, with the translation shown in English for ease of comprehension.
When evaluating ``to NYC'' the annotator looks at the translation and sees the
word ``stateside''. This word captures the whole phrase and so we mark the
structural node with an atomic label. Here we choose ``Orange'' since it approximately captures the meaning
in this context. The ability to mark structural nodes with atomic labels allows
the annotator to account for translations which only correspond at the phrase
level. Another feature highlighted in this example is that the root node is
``Adequate''. This is because the root node still has two scenes linked by one linker and
so the relationship between child nodes is maintained. There is an error caused by a wrong
translation of the linker ``After'' which translates as ``by'' and this is
marked as ``Red'', but this error is marked at the point at which it occurs.

>>>>

{\small
\begin{tabular}{|l|l|l|l|}
\hline
L & Linker &  A & Participant \\
H & Scene & R & Relator \\
P & Process & C & Centre \\
\hline
\end{tabular}
}
    \end{center}
\caption{\label{fig:ucca_example_v2}
  Sample UCCA annotation where leaves correspond to words and nodes to units.
  The dashed edge indicates that ``Tom'' is also a participant in the ``moved to NYC''
  Scene. Edge labels mark UCCA categories, listed  in the table.}
%which are largely ignored in this work
\end{figure}

@@

In Figure~\ref{fig:hume_tree_v2} we can see an example of a possible HUME
annotation, with the translation shown in English for ease of comprehension.
When evaluating ``to NYC'' the annotator looks at the translation and sees the
word ``stateside''. This word captures the whole phrase and so we mark this
non-leaf node with an atomic label. Here we choose ``Orange'' since
it approximately captures the meaning
in this context. The ability to mark non-leaves with atomic labels allows
the annotator to account for translations which only correspond at the phrase
level. Another feature highlighted in this example is that the root node is
``Adequate''. This is because the root node still has two Scenes linked by one linker and
so the relationship between child nodes is maintained. There is an error caused by a wrong
translation of the linker ``After'' which translates as ``by'' and this is
marked as ``Red'', but this error is marked at the level at which it occurs.
